Landscape composition and beneficial insects

### 2020-05-06 manuscript/manuscript_outline.Rmd
Worked on outline, esp. figures and citations

---
title: "Landscape composition and beneficial insects"
author: "Sam Robinson, Paul Galpern, others"
date: "03/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

* We don't have a good understanding of what drives arthropod abundance
  + Bees are generally driven by flower/nest abundance
  + Limited understanding of other arthropods
  + Beetles are limited by water, food, oviposition sites, etc.
  + Arachnids are similarly limited by food, shelter

* Landscape structure can influence abundance of beneficial arthropods in agricultural areas
  + No-till agriculture 
  + How can we design landscapes to benefit both farmers and insects?

* Point estimates of abundance are influenced by spatio-temporal processes 
  + Arthropods move between landscape components depending on their life history
  + e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields (Desender and Alderweireldt 1988, J. of App. Ent.)
  + Counts are a proxy of activity density, not necessarily abundance
  + Nevertheless, this is probably an OK measure (_need to justify this_)

* In this study, we used pitfall trap counts of three species of beneficial arthropod to determine how landscape composition affects activity density of arthropods
  + We hypothesized that:
  1. Abundance of semi-natural land would result in increased arthropod abundance
  2. Other things...

@@

##Data collection

@@

* To characterize landscape composition surrounding the traps, we used classified landscape data from AAFC
  + Classifications are very accurate for fields (~90%), but less accurate for non-crop areas (~70%)
  + Landscape studies often use the landscape composition within a circle of a fixed radius surrounding each point
  + However, the radius of the circle depends on the grain of the landscape that is relevant to the abundance of a given organism.
  + Instead, we divided the landscape into annuli (rings) surrounding each trap location.
  + Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.
  + Using functional regression (see below), we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition

##Statistics

* Function-on-scalar (FOS) regression is a special type of linear model ($\hat{y}=X\beta$), where the values of the coefficients ($\beta$) are defined by a smooth function
  + In our case, the coefficients represent the effect of a given type of landscape cover, and are a smooth function of distance from the trap (i.e. $\beta_i = f(distance_i)$)
  + This technique has been used by other authors; Galpern et al. called this ``onion-skin regression"
  + We fit our functional regression models using _mgcv_ version XXX.

@@

@@

>>>>

---
title: "Landscape composition and beneficial insects"
author: "Sam Robinson, Paul Galpern, et al."
date: "03/04/2020"
output: html_document
bibliography: "/home/samuel/Documents/bibtexRefs/references.bib"
csl: ecology-letters.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

@@

* We don't have a good understanding of what drives beneficial arthropod abundance
  + Bees are generally driven by flower/nest substrate availability [@roulston2011]
  + Limited understanding of other arthropods
  + Beetles are limited by water, food, and oviposition sites [@lovei1996]
  + Arachnids are similarly limited by food, shelter

* Landscape structure can influence abundance of beneficial arthropods in agricultural areas [@albrecht2010]
  + No-till agriculture is better for some ground beetles [@busch_Msc]
  + How can we design landscapes to benefit both farmers and insects?

* Point estimates of abundance are influenced by spatio-temporal processes 
  + Arthropods move between landscape components depending on their life history
  + e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields [@desender1988]
  + Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000]
* In this study, we used pitfall trap counts of three species of beneficial arthropod to determine how landscape composition affects activity density of arthropods
  + We hypothesized that:
  1. Abundance of semi-natural land (SNL) would result in increased arthropod abundance
  2. Nearby SNL acts as a source of arthropods earlier in the season, and act as a sink later on, as arthropods migrate into margins to reproduce

@@

## Data collection

@@

* To characterize landscape composition surrounding the traps, we used classified landscape data from AAFC
  + Classifications are very accurate for fields (~90%), but less accurate for non-crop areas (~70%, [@AAFC_data])
  + Landscape studies often use the landscape composition within a circle of a fixed radius surrounding each point
  + However, the radius of the circle depends on the grain of the landscape that is relevant to the abundance of a given organism.
  + Instead, we divided the landscape into annuli (rings) surrounding each trap location.
  + Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.
  + Using functional regression (see below), we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition

## Statistics

* Function-on-scalar (FOS) regression is a special type of linear model ($\hat{y}=X\beta$), where the values of the coefficients ($\beta$) are defined by a smooth function
  + In our case, the coefficients represent the effect of a given type of landscape cover, and are a smooth function of distance from the trap (i.e. $\beta_i = f(distance_i)$)
  + This technique has been used by other authors; @galpern2020 called this ``onion-skin regression"
  + We fit our functional regression models using _mgcv_ version 1.8-31.
  + @ockinger2007 is a test

@@

## _Pterostichus melanarius_

![Landscape influence on _P. melanarius_ activity density](../figures/Pterostichus_melanarius_fixeff.png)

## _Pardosa distincta_

![Landscape influence on _P. distincta_ activity density](../figures/Pardosa_distincta_fixeff.png)

## _Phalangium opilio_

![Landscape influence on _P. opilio_ activity density](../figures/Opiliones_fixeff.png)

@@

# References
